Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2023-01-09 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Alberto Guillén <aguillen@ugr.es>

We can speculate that teaching staff's opinions of chatbots are influenced by negative
experiences with chatbots used in customer support, which is what most people are likely to have
experienced. Further study may be needed to confirm this, but it is important to 
keep in mind when introducing chatbot technologies in the classroom.
To potentially change this existing perception, it will be necessary to make the chatbot as simple and satisfying to use as possible.

Regarding gender grouping, both genders agree in their uses, so it seems not
relevant at all. However, when we look at the plot containing the sector differentiation,
it is interesting to note that university teachers are more likely to use chatbots 
for grades and FAQs compared to other tertiary education teachers.
This seems reasonable as the frequency of seeing the students
is lower at the University so, an automatic tool for grade notification for
continuous evaluation would be more helpful.
Furthermore, the high student-to-teacher
ratios that university teachers often face could be another reason why
a higher number of them are willing to use chatbots for FAQs, as this could
reduce misunderstandings and email overload from students.

>>>>

We can speculate that teaching staff's opinions of chatbots are influenced by negative
experiences with chatbots used in customer support, which is what most people are likely to have
experienced. Further study may be needed to confirm this, but it is important to 
keep in mind when introducing chatbot technologies in the classroom.
To potentially change this existing perception, it will be necessary to make chatbots as simple and satisfying to use as possible.

Regarding gender grouping, both genders agree in their uses, so it seems not
relevant at all. However, when we look at the plot containing the sector differentiation,
it is interesting to note that university teaching staff are more likely to use chatbots 
for grades and FAQs compared to other tertiary education teachers.
This seems reasonable as the frequency of seeing the students
is lower at the University so, an automatic tool for grade notification for
continuous evaluation would be more helpful.
Furthermore, the high student-to-teacher
ratios that university teachers often face could be another reason why
a higher number of them are willing to use chatbots for FAQs, as this could
reduce misunderstandings and email overload from students.
